---
title: "Untitled"
author: "Syeda"
date: "2024-06-15"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r, echo = False}
library(readxl)
library(ggplot2)
library(plotly)


data <- read_excel("gender_paygap.xlsx")



data$dates <- as.Date(data$dates)
data$state <- as.factor(data$state)

date_min <- as.Date("2012-05-01")
date_max <- as.Date("2024-01-31")

p1 <- ggplot(data, aes(x=dates, y=gap, color=state))+
  geom_line()+
  scale_x_date(date_breaks = "year",
               date_labels = "%b %y",
               limits = c(date_min, date_max))+
  scale_y_continuous(limits = c(0,50))+
  theme(panel.grid.major = element_blank(),  # Remove major grid lines
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        plot.background = element_blank()) 
```

## Slide with Plot

```{r pressure}
ggplotly(p1)   
```

